\documentclass[11pt,a4paper,roman]{moderncv}       % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name

% character encoding
\usepackage[utf8]{inputenc}                        % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Lukasz}{Karolewski}
%\title{Curriculum Vitae}                         
% \address{MS Computer Science}{Warsaw University of Technology}
%\address{3069 Jayhawkers Pl, Unit 4, San Jose, CA 95136} % the "postcode city" and and "country" arguments can be omitted or provided empty
\phone{(408) 680-9149}                    
%\phone[fixed]{01234 123456}                      
%\phone[fax]{+3~(456)~789~012}                    
\email{lkarolewski@gmail.com}                     
\extrainfo{San Jose, CA}                   
% \extrainfo{\href{https://www.linkedin.com/in/lukaszkarolewski/}{LinkedIn}} 
%\photo[64pt][0.4pt]{picture} % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it and 'picture' is the name of the picture file
%\quote{Some quote}                               

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%----------------------------------------------------------------------------------
% Content
%----------------------------------------------------------------------------------

\begin{document}

\makecvtitle

\small{Technology leader with 15+ years of web development experience in both B2B and B2C environments and leading teams of up to 40. Experience running high traffic (\textasciitilde400k req/min) web application on AWS, driving A/B testing to measure user and SEO growth. Rich experience driving technology migrations without disrupting business, establishing high performing teams and driving tech excellence.}

\bigskip

\small{\textbf{Specialties} 
\begin{center}
web technologies (including spa, pwa, service worker, react) ${\cdot}$ web performance ${\cdot}$ scaling distributed systems ${\cdot}$ AWS ${\cdot}$ A/B testing ${\cdot}$ engineering management ${\cdot}$  CICD ${\cdot}$ automated testing ${\cdot}$ SEO ${\cdot}$ accessibility ${\cdot}$ internationalization ${\cdot}$ localization  
\end{center}
\bigskip

Permanent US Resident / Green Card holder

%     \item Experience designing api's for multi-client platforms  GrapqQL

\section{Experience}

\cventry{Santa Clara, CA}{Sr Manager, Engineering}{\href{https://www.realtor.com/}{Move Inc. - realtor.com}}{Oct 2016 -- present}{}{}

\begin{itemize}
    \item Responsible for web development of the www.realtor.com site. Leading up to 3~managers and 38~engineers organized into 6 teams.  
    \item Proposed, managed and delivered project that overhauled SRP experience and increased company revenue by 9\% (\textasciitilde35M).
    \item Built business case for rewriting realtor.com to React. Delivered project in time, exceeding project goals and meeting the company's annual growth goals. On average improved above the fold render time by 45\%, full page load by 40\%, decreased bounce rate by 20\%, Increased CSAT by 2 points, increased company revenue by 3\% (\textasciitilde15M)
    \item Lead rewrite of business layer API's that drove 13 person/year ongoing savings in development by spending 1 person/year of effort.
    \item Drove a 95\% reduction in number of 500 errors driving error rate from ~0.2\% to ~0.01\% which was attributed to 2 point increase in CSAT and improved SEO metrics.
    \item Collaborated with QE team to implement fully automated testing, which allowed moving from bi-weekly release to multiple daily releases, increasing number of defects leaking to production.
    \item Refined hiring process in a way that increased onsite interview hire rate from 10\% to 60\%.
    \item Lead web technologies center of excellence, raising frontend technology expertise across the company.
    \item Migrated www.realtor.com to https.
    \item Contributed to embracing data-driven culture by building experimentation program. Enabled the PM team to run over 30 experiments in the first year that in total increased company revenue by 21\%.
    \item Drove adoption of CICD reducing release time from 2 days to 1 hour.

\end{itemize}

\bigskip

\cventry{Victoria, BC}{CTO and Vice President of Engineering}{\href{https://www.telmediq.com/}{TelmedIQ}}{1 yr 5 mos ${\cdot}$ Jun 2015 -- Oct 2016}{}{}

% TelmedIQ’s unified Healthcare Communication Hub provides hospitals and healthcare systems with a mobile communication platform designed specifically to boost clinician efficiency, eliminate communication breakdowns, and improve patient safety.

% Encompassing mobile and desktop technology, TelmedIQ combines:
% \begin{itemize}
%     \item Secure text messaging;
%     \item Pager replacement;
%     \item Medical answering service;
%     \item On-call scheduling;
%     \item Nurse call; and
%     \item EHR integration.
% \end{itemize}

\begin{itemize}
    \item Joined as employee number three, created engineering organization and hired 18~engineers and 2~managers into DEV (web, android, ios, backend), QE and DevOps roles. 
    \item Built HIPAA compliant, streamlined communication workflow for healthcare providers recognized by KLAS and Gartner as \#1 vendor in the space. Solution was deployed across 100 healthcare organizations and 30,000 users, driving +2M revenue.
    \item Working with CEO on defining product strategy and establishing company culture 
    \item Negotiated contracts with customers and vendors.
    \item Responsible for the technical side of RFP's.
    \item Represented company at trade shows.
    \item Worked with research firms (KLAS and Gartner).
\end{itemize}

\bigskip

\cventry{Mountain View, CA}{Principal Software Engineer}{\href{https://www.symantec.com/}{Symantec}}{6 yrs 5 mos ${\cdot}$ Sep 2008 -- May 2015}{}{}

Enterprise Security Group
\begin{itemize}
    \item As a frontend architect I was overseeing migration of 8 Symantec cloud-based products into angular, coaching and mentoring frontend teams of those products. 
    \item Initiated `Symantec open source` ecosystem to enhance collaboration across teams. 
    \item Introduced git as an officially supported code repository, Worked with C-level executives to build cross-organizational support for the initiative, and VP level executives on implementation.
    \item Responsible for a complete redesign of a legacy web application into a bleeding edge responsive, single page application. The new version had support for branding, theming and was localized into 14 languages. Achieved 70\% code coverage in unit tests for frontend, designed and implemented e2e automation reducing number of defects by 60\%.
\end{itemize}

\medskip

Information Security Group

\begin{itemize}
    \item VIP Intelligent Authentication Services Development Team. Responsible for the design and implementation of multi-tiered enterprise web applications as well as web services. Actively participating in all phases of the software development life cycle including requirement analysis, design, implementation, and testing. Actively involved in the deployment of web application and services to data centers as well as helping resolve technical issues faced by customers while using the product.
    \item SQL query optimization
    \item Redesigned build process migrating it from Ant to Gradle reducing build time from 15~min to under 1~min. Created a new deployment model that utilized rpm and enabled fully automatic deployment. Brought down deploy time to 1~hour from 3-day manual process before.
\end{itemize}

\medskip

Internationalization team

\begin{itemize}
    \item Responsible for end to end analysis, design and implementation of i18n features for multiple products in Information Security Group.
    \item Created localization process and built tooling to automate localization. Used by 3 products to automate testing and translation into 14 languages.
\end{itemize}

\bigskip

\cventry{Warsaw, Poland}{Software Enginner}{\href{https://simple.com.pl/}{Simple S.A.}}{1 yr 1 mo ${\cdot}$ Aug 2007 -- Aug 2008}{}{}

As a part of four-member team designed and implemented the prototype of automated supply chain management system that based on inventory thresholds inquired for quotes, based on user-defined criteria picked the best bid, tracked payments and shipments. It was an extension of a well established ERP.

\bigskip

\cventry{Warsaw, Poland}{Owner}{Fast Internet}{6 yrs ${\cdot}$ Sep 2004 -- Aug 2010}{}{}

Started a business providing broadband internet to a local community of about 40 users. Built all of the systems to support operations, most notably: billing, traffic shaping, captive portal for new device registration. Sold business to a larger ISP.

\pagebreak
\section{Education}

% arguments 3 to 6 can be left empty

\cventry{Warsaw, Poland}{Master of Science in Computer Science}{\href{https://www.pw.edu.pl/engpw/University}{Warsaw University of Technology}}{2008--2010}{}{}  

\cventry{Warsaw, Poland}{Bachelor of Science in Computer Science}{\href{https://www.pw.edu.pl/engpw/University}{Warsaw University of Technology}}{2004--2008}{}{}

\bigskip

\cventry{Berkeley, CA}{Certificate, Negotiation and Influence}{\href{https://executive.berkeley.edu/programs/negotiation-and-influence}{Haas School of Business, University of California Berkeley}}{2019}{}{}

\cventry{Stanford, CA}{Course BUS 53, Leadership and Decision-Making}{\href{https://continuingstudies.stanford.edu/}{Stanford Continuing Studies, Stanford University}}{2017}{}{}

\cventry{Stanford, CA}{Course WSP 179 B, The Exceptional Leader: A Framework for Impactful Leadership}{\href{https://continuingstudies.stanford.edu/}{Stanford Continuing Studies, Stanford University}}{2017}{}{}

\cventry{Warsaw, Poland}{Certificate, IT Management and IT Governance}{\href{http://www.sgh.waw.pl/en/Pages/default.aspx}{SGH Warsaw School of Economics}}{2010--2011}{}{}

\cventry{Warsaw, Poland}{Certificate, Project Management}{\href{https://www.academyofbusiness.pl/en}{Ernst \& Young Academy of Business}}{2009}{}{}  

\section{Significant Honors}
 
\begin{itemize}
    \item Awarded CTO's 'Chief Collaborator' award at relator.com
    \item Awarded 'Top Talent' award at Symantec
    \item Awarded with three subsequent scholarships for academic performance at Warsaw University of Technology
\end{itemize}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}
